Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-06 paper/tv.tex
m

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\usepackage{enumerate}
\usepackage[utf8]{inputenc}
\usepackage{parcolumns}
\usepackage[spanish,english]{babel}
\usepackage{amsmath}
\usepackage{csquotes}
\usepackage{varwidth}
\newcommand{\key}[1]{\textcolor{purple}{\code{#1}}}
\newcommand{\jskey}[1]{\textcolor{blue}{\code{#1}}}
\newcommand{\es}{\textcolor{black}{\ensuremath{{es}}}}
\definecolor{palered-violet}{rgb}{0.86, 0.44, 0.58}
\definecolor{bittersweet}{rgb}{1.0, 0.44, 0.37}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\definecolor{persianplum}{rgb}{0.44, 0.11, 0.11}
\newcommand{\hide}[1]{}
\newcommand{\siderule}[1]{
\code{\footnotesize{\textcolor{mGray}{#1}}}}
\usepackage{adjustbox}
\usepackage{ebproof}
\usepackage{cancel}
\newcommand{\env}{\code{\mathcal{S}}}

@@

Expressions comprise simple values \code{v};
a guarded process is written as \code{[b]e} where if b is true, 
then it behaves as \code{e}, else it idles until \code{b} becomes true; 
%one-level field access \code{v.f} (rather than \code{v.f1.f2...} for the sake of simplicity), 
%data structure allocation \code{\textbf{new}\ d({v^*})},  
%local variable declaration \code{\alpha; e}, 
method calls \code{mn({x^*})}; 
variable assignments \code{\alpha}; 
%field update \code{v.f:=e}, 
expression sequences \code{e_1;e_2};
parallel composition \code{e_1 || e_2}, where \code{e_1} and \code{e_2} 
may communicate via multi-party event synchronization or shared variables. 
%conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}. 
The expression \code{ \textbf{event} [\anyevent{A}(v)] } 
raises an event \anyevent{A} parametrized with \code{v}. 
%and takes a set of 
%assignment actions \code{(x:=v)^*}. 
Furthermore, a number of timed process constructs can be used to capture common 
real-time system behavior patterns. Without loss of generality, we 
assume d is a non-negative integer constant.  $\textbf{delay} [d]$ idles for exactly $d$ 
time units. In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
$e_1$ shall occur before d time units elapse (since the process starts). 
Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
Process $\textbf{deadline} [d]\ e$ constrains $e$ to terminate before $d$ time units.

@@

%     \m{(Types)} &  \code{t}&\code{  ::= }&
% \code{d\ |\ \tau} 
% \\    
  \m{(Method\ Def.)} &  \code{meth}&\code{  ::= }&
  \code{ mn  \ {(x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}}
  \\
  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
  \\
  \m{(Expressions)} &  \code{e}&\code{  ::= }&
    \code{ v \ | \ 
    \alpha  \ | \ 
    [b]\ e \ |\ mn({v^*}) \ }
  \code{| 
 % v.f:=e \ | 
 \ e_1;e_2\ | \ e_1 || e_2 \ 
 % |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
 |\ \textbf{event} [\anyevent{A}(v)] 
 }  \\

 &   & & \code{
  | \ \textbf{delay} [d] \ 
  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
  | \ \textbf{deadline}  [d] \ e \  
  }  \\
  ~\\

@@

We remark additional process constructs (e.g. if-then-else, while, etc.) 
can be defined using the above. In this setting, clock variables are 
made implicit and hence they cannot be compared with each other 
directly, which potentially allows efficient clock manipulation and 
hence system verification.

@@

@@

To define the model, 
\code{var} is the set of program variables, 
\code{val} is the set of primitive values, 
\code{\es} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behaviour.
Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
the effects \code{\effect} take exactly \code{d} time units to complete; 
the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{[ev]} \ .

@@

\begin{figure}[]
  \vspace{-1mm}
  \renewcommand{\arraystretch}{1.2}
\small\begin{align*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%     Disjunction        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \effect_1 \vee \effect_2}  
&\m{iff}\quad & \code{d, s, \varphi \models \effect_1 } \ 
or\ \code{d, s, \varphi \models \effect_2 }  \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Empty          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s,  \varphi \models \pure{\pi}  , \empt}  
&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
\pure{True} } \ and\  \code{ \varphi {=} [] }\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Event          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}  , ev }  
&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
\pure{True} }\ and \ \varphi {=} [ev]  \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%     Concatenate        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}, (\es_1\cdot\es_2)}  
&\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
\code{ \varphi_1 {\lappend} \varphi_2 {=} \varphi}\ and\ 
\exists \code{d_1,d_2}. \  
\code{ d_1 {+} d_2 {=} d} \\
&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \es_1 }
\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \es_2 }\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    disjunction         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}  , (\es_1{\vee}\es_2)}  
&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \es_1 } 
\ or\ \code{d, s, \varphi \models \pure{\pi}  , \es_2 } \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    parallel         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi} , (ev_1{\cdot}\es_1)||(ev_2{\cdot}\es_2)}  
&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , ev_1{\cdot} (\es_1||(ev_2{\cdot}\es_2)) } 
\ or\ \code{d, s, \varphi \models \pure{\pi}  , ev_2{\cdot}((ev_1{\cdot}\es_1)||es_2)  } \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    parallel  2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi} , (ev\#t_1) || (\epsilon \# t_2)}  
&\m{iff}\quad & \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {\geq}t_2)}, (ev\#t_1) } 
\ or\ \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {<}t_2)}  , (ev\#t_1){\cdot}(\epsilon \# (t_2\text{-}t_1))  } \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    t times         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}  ,\es\# t}  &\m{iff}\quad &
 \code{\llbracket \pure{\pi}  , t {=} 0 \rrbracket_{s} {=}  
 \pure{True} }, \ \code{d, s, \varphi \models \pure{\pi}  , \empt}\ or  \\
& & &  \code{\llbracket \pure{\pi}, t {>} 0 \rrbracket_{s} {=}  
\pure{True} }, 
\  \exists \code{\es_1,\es_2}. \  \code{ es_1 {\cdot}  es_2 {=} es}\\
&&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi {\wedge}t_1{+} t_2{=}t)}  , 
(es_1\#t_1) {\cdot} (es_2\#t_2) } \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    star         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}, \es^\star}  &\m{iff}\quad & 
\code{d, s, \varphi \models \pure{\pi}  , \empt}\ or \ 
\code{d, s, \varphi \models \pure{\pi}  , es {\cdot} \es^\star}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    FALSE         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
& \code{d, s, \varphi \models false}  &\m{iff}\quad &
 \code{\llbracket \pure{\pi}  \rrbracket_{s} {=} \pure{False} } \ or \ \code{\varphi {=} \bott}
\end{align*}
  \vspace{-2mm}
\caption{Semantics of \timedEffects .}
\label{fig:Sementic}
\vspace{-2mm}
\end{figure}

@@

In this section, we give an axiomatic semantics model\footnote{Based on the operational semantics of Esterel and JavaScript's asynchrony formally defined in \cite{berry1992esterel} and  \cite{madsen2017model} respectively.} for the core language \code{\timedL}, by formalising a set of forward inductive rules. 
These rules transfer program states and systematically accumulate the effects syntactically. 
To define the model, we introduce a stack \env\ and describe a program state in a four-elements tuple \code{\langle \Pi, H, T \rangle}, with the following concrete domains:
\begin{flalign*}
\Pi {\defeq} t {\rightarrow} \pi, \qquad\qquad
H  {\defeq} es, \qquad\qquad
T {\defeq} t, \qquad\qquad
\env {\defeq} \code{var {\rightarrow} val }
\end{flalign*}

@@

%We describe the input and output histories of ESTEREL programs by streams carrying sets of signals.

%which is used for the description of a reactive program.

%The main difficulty in giving a semantics to \code{\timedL} consists in the idea of instantaneous reactions of ESTEREL programs to input signals.

%We base this semantics on a functional model of behaviour. We describe the input and output histories of ESTEREL programs by streams carrying sets of signals.

%we mainly present the forward verifier
% based on the syntax of each statement.

%We present the intermediate representation of program states in \figref{fig:intermediate_representation}

%\noindent   the second element represents the  containing the path constraints (\code{\pi}) and signal assignments (\code{\phi})\footnote{The difference between \code{\textbf{S} = \theta} and \code{\textbf{S} \mapsto \theta } is: the former one denotes the constraints along the execution path, which creates \emph{false} if there are two different status assignments to the same signal; while the latter one records the current status of one signal, and will be overwritten when the presence of a signal had been determined.};

>>>>

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\usepackage{enumerate}
\usepackage[utf8]{inputenc}
\usepackage{parcolumns}
\usepackage[spanish,english]{babel}
\usepackage{amsmath}
\usepackage{csquotes}
\usepackage{varwidth}
\newcommand{\key}[1]{\textcolor{purple}{\code{#1}}}
\newcommand{\jskey}[1]{\textcolor{blue}{\code{#1}}}
\newcommand{\es}{\textcolor{black}{\ensuremath{{es}}}}
\definecolor{palered-violet}{rgb}{0.86, 0.44, 0.58}
\definecolor{bittersweet}{rgb}{1.0, 0.44, 0.37}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\definecolor{persianplum}{rgb}{0.44, 0.11, 0.11}
\newcommand{\hide}[1]{}
\newcommand{\siderule}[1]{
\code{\footnotesize{\textcolor{mGray}{#1}}}}
\usepackage{adjustbox}
\usepackage{ebproof}
\usepackage{cancel}
\newcommand{\env}{\code{\mathcal{V}}}

@@

Expressions comprise simple values \code{v};
a guarded process is written as \code{[b]e} where if b is true, 
then it behaves as \code{e}, else it idles until \code{b} becomes true; 
%one-level field access \code{v.f} (rather than \code{v.f1.f2...} for the sake of simplicity), 
%data structure allocation \code{\textbf{new}\ d({v^*})},  
%local variable declaration \code{\alpha; e}, 
method calls \code{mn({x^*})}; 
%variable assignments \code{\alpha}; 
%field update \code{v.f:=e}, 
expression sequences \code{e_1;e_2};
parallel composition \code{e_1 || e_2}, where \code{e_1} and \code{e_2} 
may communicate via multi-party event synchronization or shared variables; 
conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}.

The expression \code{ \textbf{event} [\anyevent{A}(v,  \alpha^*)] } 
raises an event \anyevent{A} parametrized with \code{v}, 
and takes a set of 
assignment actions \code{\alpha^*}. 
Furthermore, a number of timed process constructs can be used to capture common 
real-time system behavior patterns. Without loss of generality, we 
assume d is a non-negative integer constant.  $\textbf{delay} [d]$ idles for exactly $d$ 
time units. In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
$e_1$ shall occur before d time units elapse (since the process starts). 
Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
Process $\textbf{deadline} [d]\ e$ constrains $e$ to terminate before $d$ time units.

@@

%     \m{(Types)} &  \code{t}&\code{  ::= }&
% \code{d\ |\ \tau} 
% \\    
  \m{(Method\ Def.)} &  \code{meth}&\code{  ::= }&
  \code{ mn  \ {(x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}}
  \\
  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
  \\
  \m{(Expressions)} &  \code{e}&\code{  ::= }&
    \code{ v \ | \ 
    [b]\ e \ |\ mn({v^*}) \ }
  \code{| 
 % v.f:=e \ | 
 \ e_1;e_2\ | \ e_1 || e_2 \ 
  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
 }  \\

 &   & & \code{
  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
  | \ \textbf{delay} [d] \ 
  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
  | \ \textbf{deadline}  [d] \ e \  
  }  \\
  ~\\

@@

In this setting, clock variables are 
made implicit and hence they cannot be compared with each other 
directly, which potentially allows efficient clock manipulation and 
hence system verification.

@@

\begin{flalign*}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%   deadline                 %%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \code{\frac{
    V \not\models  b 
  }{(V, [b] \ e ) \xrightarrow[]{t} (V, [b] \ e)}\ [gu_1]} 
  \quad
  \code{\frac{
    V \models  b 
  }{(V, [b] \ e ) \xrightarrow[]{\tau} (V, e)}\ [gu_2]} 
  \quad
  \code{\frac{
  }{(V, \alpha ) \xrightarrow[]{\tau} (\alpha(V), ())}\ [assign]} 
\end{flalign*}

\begin{flalign*}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%   deadline                 %%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \code{\frac{
    (V,e_1) \xrightarrow[]{\anyevent{A}} (V^\prime,e_1^\prime) 
  }{(V, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (V^\prime, e_1^\prime || e_2)}\ [pa_1]} 
  \quad  
  \code{\frac{
    (V,e_2) \xrightarrow[]{\anyevent{A}} (V^\prime,e_2^\prime) 
  }{(V, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (V^\prime, e_1 || e_2^\prime)}\ [pa_2]} 
\quad
\code{\frac{
  (V,e_1) \xrightarrow[]{\anyevent{A}/\tau} (V^\prime,e_1^\prime) 
}{(V, e_1; e_2 ) \xrightarrow[]{\anyevent{A}/\tau} (V^\prime, e_1^\prime ; e_2)}\ [se]} 
\end{flalign*}

@@

To define the model, 
\code{var} is the set of program variables, 
\code{val} is the set of primitive values, 
\code{\es} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behaviour.
Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
the effects \code{\effect} take exactly \code{d} time units to complete; 
the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{ev^*} \ .

@@

\begin{figure}[]
  \vspace{-1mm}
  \renewcommand{\arraystretch}{1.2}
\small\begin{align*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%     Disjunction        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \effect_1 \vee \effect_2}  
&\m{iff}\quad & \code{d, s, \varphi \models \effect_1 } \ 
or\ \code{d, s, \varphi \models \effect_2 }  \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Empty          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s,  \varphi \models \pure{\pi}  , \empt}  
&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
\pure{True} } \ and\  \code{ \varphi {=} [] }\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         Event          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}  , ev }  
&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
\pure{True} }\ and \ \varphi {=} [ev]  \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%     Concatenate        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}, (\es_1\cdot\es_2)}  
&\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
\code{ \varphi_1 {\lappend} \varphi_2 {=} \varphi}\ and\ 
\exists \code{d_1,d_2}. \  
\code{ d_1 {+} d_2 {=} d} \\
&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \es_1 }
\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \es_2 }\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    disjunction         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}  , (\es_1{\vee}\es_2)}  
&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \es_1 } 
\ or\ \code{d, s, \varphi \models \pure{\pi}  , \es_2 } \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    parallel         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi} , (ev_1{\cdot}\es_1)||(ev_2{\cdot}\es_2)}  
&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , ev_1{\cdot} (\es_1||(ev_2{\cdot}\es_2)) } 
\ or\ \code{d, s, \varphi \models \pure{\pi}  , ev_2{\cdot}((ev_1{\cdot}\es_1)||es_2)  } \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    parallel  2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi} , (ev\#t_1) || (\epsilon \# t_2)}  
&\m{iff}\quad & \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {\geq}t_2)}, (ev\#t_1) } 
\ or\ \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {<}t_2)}  , (ev\#t_1){\cdot}(\epsilon \# (t_2\text{-}t_1))  } \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    t times         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}  ,\es\# t}  &\m{iff}\quad &
 \code{\llbracket \pure{\pi}  , t {=} 0 \rrbracket_{s} {=}  
 \pure{True} }, \ \code{d, s, \varphi \models \pure{\pi}  , \empt}\ or  \\
& & &  \code{\llbracket \pure{\pi}, t {>} 0 \rrbracket_{s} {=}  
\pure{True} }, 
\  \exists \code{\es_1,\es_2}. \  \code{ es_1 {\cdot}  es_2 {=} es}\\
&&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi 
{\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)}  , 
(es_1\#t_1) {\cdot} (es_2\#t_2) } \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    star         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, s, \varphi \models \pure{\pi}, \es^\star}  &\m{iff}\quad & 
\code{d, s, \varphi \models \pure{\pi}  , \empt}\ or \ 
\code{d, s, \varphi \models \pure{\pi}  , es {\cdot} \es^\star}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    FALSE         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
& \code{d, s, \varphi \models false}  &\m{iff}\quad &
 \code{\llbracket \pure{\pi}  \rrbracket_{s} {=} \pure{False} } \ or \ \code{\varphi {=} \bott}
\end{align*}
  \vspace{-2mm}
\caption{Semantics of \timedEffects .}
\label{fig:Sementic}
\vspace{-2mm}
\end{figure}

@@

\newcommand{\s}[1]{\code{\{ #1\}}}

We here present the forward verification rules, s
which are used to systematically accumulate the effects based on 
the syntax of each statement.
\code{\mathcal{P}} denotes the program being checked. 
With pre/post conditions declared for each method in \code{\mathcal{P}}, 
we can apply modular verification to a method's body using Hoare-style 
triples \code{ \Pi, \env \vdash \s{ \effect_c} \ e\ \s{\effect_c^\prime}}
where 
\code{\Pi} is the current guard, 
\code{\env} is the current valuation of the variables;
\code{\effect_c} is the current effects, 
and \code{ \effect_C^\prime}
is the resulting effects by executing \code{e}.

\begin{comment}
  In this section, we give an axiomatic semantics model\footnote{Based on the operational semantics of Esterel and JavaScript's asynchrony formally defined in \cite{berry1992esterel} and  \cite{madsen2017model} respectively.} for the core language \code{\timedL}, by formalising a set of forward inductive rules. 
These rules transfer program states and systematically accumulate the effects syntactically.

To define the model, we introduce a stack \env\ and describe 
a program state in a four-elements tuple \s{H, G}, with the following concrete domains:
\begin{flalign*}
G {\defeq} \pi, \qquad\qquad
H  {\defeq} es, \qquad\qquad
\env {\defeq} \code{var {\rightarrow} val }
\end{flalign*}

@@

  v \ | \ 
    [b]\ e \ |\ mn({v^*}) \ }
  \code{| 
 % v.f:=e \ | 
 \ e_1;e_2\ | \ e_1 || e_2 \ 
  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
 }  \\

 &   & & \code{
  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
  | \ \textbf{delay} [d] \ 
  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
  | \ \textbf{deadline}  [d] \ e \  
\end{comment}

\begin{gather*}
  \code{\frac{\effect_C^\prime {=} \effect_C\cdot \anyevent{a}}{\vdash \{  \effect_C \}\  \textbf{event} [\anyevent{a}] \ \{ \effect_C^\prime \}} \   {[FV\text{-}Event]}} 
  \qquad
  \code{\frac{\vdash \{ \effect_C\}\ e_1 \ \{  \effect_C^\prime\} \qquad \vdash \{  \effect_C^\prime\}\ e_2 \ \{  \effect_C^{\prime\prime}\} }{\vdash \{  \effect_C\}\  e_1;e_2 \ \{  \effect_C^{\prime\prime}\}} \  {[FV\text{-}Seq]}}  
\end{gather*}

\begin{gather*}
\code{\frac{ \vdash \{  v \wedge \effect_C  \} \ e_1 \ \{  \effect_C^{\prime}\} \qquad \vdash \{ \neg v \wedge \effect_C \} \ e_2 \ \{  \effect_C^{\prime\prime}\}  }
{\vdash \{  \effect_C\}\  \textbf{if}\ v\ \textbf{then}\ e_1\ \textbf{else}\ e_2 \ \{  \effect_C^{\prime} \vee\effect_C^{\prime\prime} \} } \  {[FV\text{-}If\text{-}Else]}} 
\end{gather*}

\begin{gather*}
\code{\frac{
\begin{matrix}
\text{\code{  \tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
\\
\text{\code{\vdash rev( \effect_C) \CONTAIN rev([y^*/x^*] \effect_{pre})   \qquad   \effect_C^\prime =  \effect_C \cdot  [y^*/x^*]\effect_{post}}}
\end{matrix}}
{\vdash \{  \effect_C \} \  mn({y^*})  \ \{  \effect_C^\prime\}} \ {[FV\text{-}Call]}}
\end{gather*}

\begin{gather*}
\code{\frac{  \vdash \{  \empt \}  \ e \  \{ \effect_C \} \qquad\qquad  \vdash\effect_C \CONTAIN   \effect_{post}}{  \vdash \tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}} \ {[FV\text{-}Meth]}}  
\end{gather*}
